Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-30 tese2/architecture.tex
[ADD] optimal ratio confidence intervals
[ADD] chapter summary

\begin{table}[H]
\centering
	\caption{Application Architecture}
	\label{table:apparch}
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[12pt]\cline{1-5}\cline{7-7}
\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{~~~~~ot.js~~~~~} & \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} & \multicolumn{1}{c|}{adapter.js} &   \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} &\\[12pt]\hline
\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[12pt]\hline
\end{tabular}
	        \label{fig:apparch}
\end{table}

Figure~\ref{fig:apparch} presents the application architecture and the underlying technologies seen from the user's perspective. \emph{Adapter.js} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.

@@

>>>>

\begin{table}[H]
\centering
	\caption{Application Architecture}
	\label{table:apparch}
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[12pt]\cline{1-5}\cline{7-7}
\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{~~~~~ot.js~~~~~} & \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} & \multicolumn{1}{c|}{adapter.js} &   \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} &\\[12pt]\hline
\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[12pt]\hline
\end{tabular}
\end{table}

Table~\ref{table:apparch} presents the application architecture and the underlying technologies seen from the user's perspective. \emph{Adapter.js} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.

@@

\section{Chapter Summary}
\label{architecture:summary}

In this chapter we have shown the modules needed in order to implement our solution.

Several technologies were taken into account for implementing each module, we have studied the pros and cons of each technology and decided the architecture for our solution.

### 2016-04-30 tese2/evaluation.tex
[RFT] gnuplot confidence intervals
[ADD] chapter summary

@@

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.45\linewidth}
  \begin{center}
    \input{stats/user_times.tex}
  \end{center}
  \caption{Time spent per task}
  \label{fig:user_times}
\end{minipage}
\begin{minipage}[b]{0.45\linewidth}
   \begin{center}
    \input{stats/user_clicks.tex}
  \end{center}
  \caption{Mouse clicks per task}
  \label{fig:user_clicks}
\end{minipage}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.45\linewidth}
  \begin{center}
    \input{stats/user_errors.tex}
  \end{center}
  \caption{Errors per task}
  \label{fig:user_errors}
\end{minipage}
\begin{minipage}[b]{0.45\linewidth}
  \begin{center}
    \input{stats/user_diffs.tex}
  \end{center}
  \caption{Difficulty per task}
  \label{fig:user_diffs}
\end{minipage}
\end{figure}

\begin{table}[H]
\centering
\caption{Metrics for an experienced user}
\label{table:optimal}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Task} & 1 & 2 & 3 & 4 & 5 \\ \hline
\textbf{Time} & 20 & 35 & 30 & 25 & 35 \\ \hline
\textbf{Clicks} & 7 & 10 & 5 & 9 & 7 \\ \hline
\end{tabular}
\end{table}

[COMPARE WITH MINIMAL RESULTS (best clicks, best time, no errors)]

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/user_evals.tex}
  \end{center}
  \caption{Solution evaluation}
  \label{fig:user_evals}
\end{figure}

@@

>>>>

\begin{table}[H]
\centering
\caption{Metrics for an experienced user}
\label{table:optimal}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Task} & 1 & 2 & 3 & 4 & 5 \\ \hline
\textbf{Duration (seconds)} & 20 & 35 & 30 & 25 & 35 \\ \hline
\textbf{Number of clicks} & 7 & 10 & 5 & 9 & 7 \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{stats/user_times.eps}
    \caption{Time spent per task}
    \label{fig:user_times}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{stats/user_clicks.eps}
    \caption{Mouse clicks per task}
    \label{fig:user_clicks}
\end{minipage}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{stats/user_errors.eps}
  \caption{Errors per task}
  \label{fig:user_errors}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{stats/user_diffs.eps}
  \caption{Difficulty per task}
  \label{fig:user_diffs}
\end{minipage}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/user_evals.eps}
  \caption{Solution evaluation}
  \label{fig:user_evals}
\end{figure}

@@

\section{Chapter Summary}
\label{evaluation:summary}

In this chapter we describe the test scenarios that we have created in order to evaluate our system.

The performance tests revealed unexpected results which were crucial to find and solve performance issues. Another important aspect of our performance test results, were the understanding of how data flows between our system modules.

In respect to user interface tests, we have obtained valuable feedback that we used to improve our prototype's usability.

In order to understand how good the results were for each performed task, we have defined optimal values for the different metrics. In general the results reveal a significant difference between observed values and optimal values which can be explained by the users lack of experience with systems such as we have created.
